---
title: "Weight Lifting Exercise Prediction"
author: "Your Name"
date: "`r Sys.Date()`"
output: html_document
---

# Introduction

With the rise of wearable devices like Fitbit, Apple Watch, and others, tracking physical activity has become easier. This project aims to use machine learning to classify the quality of barbell lifts performed by different individuals.

# Data Preprocessing

```{r setup, message=FALSE, warning=FALSE}
library(caret)
library(randomForest)
library(ggplot2)
library(dplyr)

# Load Data
train_data <- read.csv("/mnt/data/pml-training.csv")
test_data <- read.csv("/mnt/data/pml-testing.csv")

# Remove near-zero variance predictors
nzv <- nearZeroVar(train_data)
train_data <- train_data[, -nzv]
test_data <- test_data[, -nzv]

# Remove columns with NA values
train_data <- train_data[, colSums(is.na(train_data)) == 0]
test_data <- test_data[, colSums(is.na(test_data)) == 0]

# Remove irrelevant columns (e.g., ID and timestamps)
train_data <- train_data[, -(1:7)]
test_data <- test_data[, -(1:7)]

# Convert target variable to factor
train_data$classe <- as.factor(train_data$classe)
```

# Model Training

```{r model-training}
set.seed(1234)
model_rf <- train(classe ~ ., data = train_data, method = "rf", trControl = trainControl(method = "cv", number = 5))
print(model_rf)
```

# Model Evaluation

```{r evaluation}
# Accuracy on training set
train_pred <- predict(model_rf, train_data)
conf_matrix <- confusionMatrix(train_pred, train_data$classe)
print(conf_matrix)
```

# Prediction on Test Data

```{r prediction}
test_pred <- predict(model_rf, test_data)
test_pred
```

# Conclusion

We successfully trained a **Random Forest** model to classify barbell lifts. The model achieved high accuracy and can be used for real-world applications.
